Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-07-09 Referee1_Response.tex

%%%%%%%%%%%%%%%%%
%% Need to be careful with the minor changes. Will these be affected?
%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
%%    - GB
%%%%%%%%%%%%%%%%%

\noi  
{\large \bf ``Major'' comments:}
\medskip

\begin{itemize}
\item[\textbf{M1.}] \textit{In the typical simulation setting, the computational effort required to produce the output dominates, and hence one would like to ``make the most'' of the output in terms of analysis. 
Sometimes, a similar motivation can arise in stochastic optimization because there may be a computationally expensive underlying simulation model that must be run to produce the i.i.d.\ realizations that are then used in an SAA approach. 
(While they don't now, the authors could include this as motivation for
their work.)}
\end{itemize}

\noi
%We thank the referee for this suggestion. 
Thank you for this suggestion. 
You are right.
There are cases when generating scenarios is expensive in the stochastic optimization setting as well. 
We changed the introduction based on your, the associate editor and the other reviewer's comments. 
We specifically added this as a motivation. 
The motivation now appears in the first full paragraph on page 4 of the paper. 
\medskip

@@

\begin{itemize}
\item[] \textit{However, perhaps more often, sampling the i.i.d. realizations is computationally cheap compared to solving the resulting SAA instances in stochastic optimization. 
In this latter case, we have a choice between simply increasing the number of batches in a non-overlapping method or using the overlapping batch means approach (with some degree of overlap) in order to reduce variance.
Based on the paper's results, perhaps the computational effort required to achieve a level of variance reduction should guide this choice. 
The authors do point to the fact that warm starts in a stochastic
optimization algorithm can be exploited much more easily when using overlapping batch means than when not using overlapping batches. 
Some attempt to explore this tradeoff would be valuable. 
The computational results use sorting (for the news vendor problem), a dynamic programming algorithm (for a stochastic knapsack model), and a decomposition method (for two-stage stochastic linear programs). 
While I am not suggesting that this exploration needs to be made for all three types of algorithms, even exploring it in the case of the sorting algorithm (where some algorithms are well suited for almost-sorted lists) could provide valuable insight.}
\end{itemize}

\noi 
We studied computational efficiency of the OMRP variance estimators and demonstrated efficiency on the newsvendor problem using insertion sort. 
The results of this study are presented in a new section, \S 5.4 (Computational Efficiency).
%We studied the computational efficiency of the OMRP estimators, based on your and the associate editor's comments, and provided a summary of our results in a new section, Section 5.4 (Computational Efficiency). 
We first approached efficiency by the reciprocal of variance multiplied by the computation time, per the associate editor's suggestion. 
Maximizing computational efficiency defined in this manner provided guidelines on selecting the degree of overlap. 
We then looked at how OMRP compared to increasing the number batches in MRP to reach an equivalent variance level.
We examined computational efficiency theoretically, assuming a functional form of the solution time per batch, and also empirically. 
For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions; thank you. 
We found that when effective warm-starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.  
%All these results are presented in Section 5.4 (Computational Efficiency). 
%Thank you for this suggestion. 
We believe the study of computational efficiency significantly improved the paper. 
Thank you.\smallskip

\noi
{\it Note:} Please also see our response to your minor comment 19 below.
\medskip

@@

\begin{itemize}
\item[4.] \textit{p3, l38: Suggest: estimator of the optimality gap \ldots}
\end{itemize}

\noindent 
Done.
\medskip

\begin{itemize}
\item[5.] \textit{p4, l34: Suggest: once the data are generated through a simulation, they \ldots}
\end{itemize}

\noindent 
Done. 
\smallskip

\noi 
{\it Note:} This sentence now appears in the second paragraph of Section 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee. 
\medskip

@@

\begin{itemize}
\item[6.] \textit{p4, l42: Suggest: Partial overlap results in fewer batches, hence fewer optimization \ldots}
\end{itemize}

\noindent 
We removed this sentence and replaced it with a shorter one in order to improve exposition. 
We used `smaller number of batches' based on the comments of the other referee in the new sentence. 
\smallskip

\noi 
{\it Note:} This section now appears in the second paragraph of Section 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee. 
\medskip

@@

\begin{itemize}
\item[7.] \textit{p6, l32: Suggest: The degrees \ldots make \ldots}
\end{itemize}

\noindent 
Done.

XXXX Denominator term makes!  I think it changed to denominator term. CHECK XXXX
\medskip

### 2014-07-09 omrp_lb_rev.tex
Major rewrite of Introduction
1) Wrote a motivation paragraph
2) Wrote a list of contributions
3) Wrote differences of this paper compared to WSC version
4) Moved a paragraph from Intro to Overlapping Batch Means section and
edited that paragraph
5) Changed Referee 1 response accordingly
6) Added a reference
7) Some other minor minor changes

The Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts. 
In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
\cite{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \citep{Meterelliyoz_etal_12}.
To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.

A natural setting where batch means are used in stochastic optimization (especially in stochastic programming) is for assessing solution quality. 
This typically involves generating point and interval estimators of the optimality gap of a given candidate solution using Monte Carlo simulation. 
Because optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonoverlapping batches of data to generate a number of optimality gap estimators. 
These individual estimators are then used to form point and interval estimators applying the nonoverlapping batch means method.
This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
In this paper, we formulate an overlapping batches version of MRP, allowing for partial overlap, and provide conditions under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
We also show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
We also present computational results to examine small-sample behavior. 
Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.

We consider a stochastic optimization problem of the form 
\begin{align} \tag{SP} \label{eq:sto_prog} 
	z^* & = \min_{\x \in X} \e{f(\x,\xit)},
\end{align}
where $\x$ is a vector of decision variables, $\xit$ is a vector of random variables, and $X$ is the feasible set, which consists of only deterministic constraints. 
There are no stochastic constraints such as probabilistic or expected-value constraints. 
Further, it is assumed that the distribution of $\xit$ is known and that we can sample from it.
Even though we will impose a more-restrictive moment condition later, we assume that $\e{f(\x,\xit)}$ is well defined and finite for all $\x \in X$ and (\ref{eq:sto_prog}) has a finite optimal solution achieved on $X$.

@@

We wish to assess the quality of a candidate solution $\xh \in X$, which may have been found in any way.
Assessing solution quality is important in practice because as (\ref{eq:sto_prog}) typically cannot be solved exactly, one only has an approximate solution $\xh$ without verification of its quality.
Assessing solution quality is also a critical component of stopping criteria in algorithms designed to (approximately) solve (\ref{eq:sto_prog}).
We define the quality of $\xh$ by its optimality gap, $\e{f(\xh,\xit)} - \zs$. 
The lower the optimality gap, the higher the quality of the solution; and a zero optimality gap implies that the solution is optimal. 
We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout this paper.

@@

Our aim is to apply the idea of overlapping batches to MRP.  
Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
%Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
We note several differences in this setting compared to the classical simulation setting.  
In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
We are interested in estimating the variance of an optimality gap estimator.  
An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
%For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
%Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
The nonoptimized counterparts are (regular) overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions. 
We establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.  
In this setting, due to the need to solve a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
This can be alleviated in two ways. 
First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
% THIS LAST SENTENCE NEEDS TO CHANGE!

@@

The rest of the paper is organized as follows.  
In the next section, we review relevant background information.  
We first discuss overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP CIs, and that the OMRP variance estimators have lower variances than their nonoverlapping counterparts---the MRP estimators.
In \S \ref{sec:comp}, we test the performance of OMRP on four problems and end in \S \ref{sec:concl} with a summary and conclusions.

@@

Overlapping batch means reuses a subset of the observations from one batch to form the next batch. 
As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
In the nonoverlapping case, there are only two batches:
% the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
$y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$, and so on.  
This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
It is possible to vary the amount of overlap between neighboring batches. 
This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
The overlapping batch means 
%formed using the batch nonoverlap parameter $1 \leq \gamma < m$ 
are no longer independent. 
However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
%the overlapping estimator has 
a lower asymptotic variance than its nonoverlapping counterpart.

@@

The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $0\leq \gamma< m$ relative its nonoverlapping counterpart 
%$\var{\vtm{\ybb}}$ 
depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$. 
The maximally-overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
\cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally-overlapping cases. 
Under appropriate conditions, these results, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
\begin{equation}
\label{eq:varvarred}
\frac{n}{m}\var{n \vartg{\ybb}} \rightarrow \beta_{\gammab} \sigma^4
\end{equation}
as the batch size $m$ and then the number of batches $n/m$ tend to infinity. 
In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches, $\beta_0 = \frac{4}{3}$ for maximally overlapping batches, and more generally, $\beta_{\gammab}$ is twice the value of 
\begin{equation} \label{eq:var_reduct_formula}
	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right),
\end{equation}
where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument.
If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
This means that the maximally-overlapping variance estimator has a variance that is two-thirds ($66.67\%$) of the nonoverlapping estimator.
As the amount of overlap decreases, the variance increases. 
When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/2$), for instance, the variance is 75\% of the nonoverlapping counterpart.

@@

The minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI.  
See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.

@@

@@

\begin{figure}[htb!]
	\centering
	\begin{tabular}{*{18}{c}}
		$\xit^1$ & $\xit^2$ & $\xit^3$ & $\xit^4$ & $\xit^5$ & $\xit^6$ & $\xit^7$ & $\xit^8$ & $\xit^9$ & $\xit^{10}$ & $\xit^{11}$ & $\xit^{12}$ & $\xit^{13}$ & $\xit^{14}$ & $\xit^{15}$ & $\xit^{16}$ & $\xit^{17}$  & $\xit^{18}$ \\
% 		First Set of Batches
		\multicolumn{6}{l}{[---------------1-----------------]} &
		\multicolumn{6}{l}{[-----------------4------------------]} &
		\multicolumn{6}{l}{[------------------7--------------------]} \\
% 		Third set of Batches
		& & \multicolumn{6}{l}{[---------------2-----------------]} &
		\multicolumn{6}{l}{[------------------5--------------------]} \\
% 		Fifth set of Batches
		& & & & \multicolumn{6}{l}{[---------------3-----------------]} &
		\multicolumn{6}{l}{[------------------6--------------------]} \\
	\end{tabular}
	\caption{Visual representation of overlapping batches with $n = 18$, $m = 6$, and $\gamma = 2$.  
        The brackets show which observations are used in each batch, and the numbers inside each bracket show the batch number $j$.}
	\label{fig:overlap_nonint}
\end{figure}

The results on overlapping batch means, discussed in Section \ref{ssec:overlap}, occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$, as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  
In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
Now we are ready to define the estimators for OMRP.
\begin{align}
	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
	VG_l & = \dfrac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
\end{align}

@@

The motivation behind forming $\gbb_l$ by taking into account $B(i)$ is to give each observation $\xit^i$ equal weight. 
This is because we want to be as close to a standard mean estimator (e.g., $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^i$) as possible.
With this definition of $\gbb_l$, when $\xs_j= \xs$ for all $j= 1, 2, \dots, \nbl$, we have $\gbb_l$ equal to its nonoptimized counterpart given in (\ref{eq:dbb}), which is the standard mean estimator. 
This fact is key in establishing the theoretical results presented in the next section. 
We note, however, that this choice of $\gbb_l$ may not be guaranteed to be nonnegative.
In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping. 
%In our computational results, however, we did not observe any negative values of $\gbb_l$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymptotic Validity of the Confidence Intervals}

>>>>

The Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts. 
In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
\cite{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \citep{Meterelliyoz_etal_12}.
To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
In this paper, we show that the same benefits of nearly the same bias and lower variances relative to nonoverlapped counterparts can be obtained from overlapping batches when used in a stochastic optimization setting.

A natural setting where batch means are used in stochastic optimization (especially in stochastic programming) is for assessing solution quality. 
This typically involves generating point and interval estimators of the optimality gap of a given candidate solution using Monte Carlo simulation. 
Because optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonoverlapping batches of data to generate a number of optimality gap estimators. 
These individual estimators are then used to form point and interval estimators applying the nonoverlapping batch means method.
This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
In this paper, we formulate an overlapping batches version of MRP with a parametrized degree of overlap.
%, and present theoretical and computational results.

We consider a stochastic optimization problem of the form 
\begin{align} \tag{SP} \label{eq:sto_prog} 
	z^* & = \min_{\x \in X} \e{f(\x,\xit)},
\end{align}
where $\x$ is a vector of decision variables, $\xit$ is a vector of random variables, and $X$ is the feasible set, which consists of only deterministic constraints. 
We assume (\ref{eq:sto_prog}) has no stochastic constraints such as probabilistic or expected-value constraints. 
Further, it is assumed that the distribution of $\xit$ is known and that we can sample from it.
Even though we will impose a more-restrictive moment condition later, we assume that $\e{f(\x,\xit)}$ is well defined and finite for all $\x \in X$ and (\ref{eq:sto_prog}) has a finite optimal solution achieved on $X$.

@@

We wish to assess the quality of a candidate solution $\xh \in X$, which may have been found in any way.
Assessing solution quality is important in practice because as (\ref{eq:sto_prog}) typically cannot be solved exactly, one only has an approximate solution $\xh$ without verification of its quality.
Assessing solution quality is also a critical component of stopping criteria in algorithms designed to (approximately) solve (\ref{eq:sto_prog}).
We define the quality of $\xh$ by its optimality gap, $\e{f(\xh,\xit)} - \zs$. 
The lower the optimality gap, the higher the quality of the solution; and a zero optimality gap implies that the solution is optimal. 
We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout the paper.

@@

Our aim is to apply the idea of overlapping batches to MRP.  
The motivation behind using overlapping in this context is twofolds. 
First, overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
%Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
Second, in some cases, generating the realizations $\xit^1, \xit^2, \dots$ to form sampling approximations of (\ref{eq:sto_prog}) can be computationally expensive and overlapping makes the most of the generated observations.

%The following are four specific contributions of this article. 
The contributions of this article are as follows. 
\begin{itemize}
\item[(i)] We formulate an overlapping batch means variant of MRP, where the degree of overlap can be chosen by the user. 
%This paper applies OBM to assessing solution quality in stochastic optimization. 
%Specifically, an overlapping batch means variant of MRP is formulated, where the degree of overlap can be chosen by the user. 
This application of OBM is novel because each batch mean estimator includes an internal minimization, which has not been studied in the literature.
%\vspace*{-0.1in}

\item[(ii)] We provide conditions under which the resulting optimality gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
We show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
These results require new proofs because of the presence of the optimization operator.

\item[(iii)] We  present computational results to examine small-sample behavior. 
Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.

\item[(iv)] As the degree of overlap increases, the number of batches and optimization problems solved increases because we need to solve a sampling problem per batch. 
At the same time, variances of the estimators are lowered, and when warm starting is available, solution time per batch can decrease, resulting in efficiency gains. 
We explore the trade-off between computation time and lower variances.
% and efficiency gains. 
%We explore the overall computation time versus lower variances and efficiency gains trade-off. 
We provide guidelines on selecting the degree of overlap based on computational efficiency and demonstrate efficiency on a newsvendor problem. 
\end{itemize}

An earlier version of the paper appeared in \citep{love2011overlapping}. 
This paper contains a number of additional results. 
% compared to its earlier conference proceedings version. 
Most of the theoretical results are new, including asymptotically lower variances of the overlapping estimators, asymptotic validity of the interval estimators, and the {\it almost sure} convergence of the variance estimator. 
These results are achieved through an assumption on the fast rate of convergence of the sampling problem's solution to the unique optimal solution, which is satisfied by several classes of (\ref{eq:sto_prog}); see \S \ref{subsec:assumptions}.
We also present additional computational results, including those from a large-scale problem, and study computational efficiency of the overlapping MRP method.

The rest of the paper is organized as follows.  
In the next section, we review relevant background information.  
We first discuss nonoverlapping and overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP CIs, and establish that the OMRP variance estimators have lower variances than their nonoverlapping MRP counterparts.
In \S \ref{sec:comp}, we test the performance of OMRP on four problems and study computational efficiency. 
We end in \S \ref{sec:concl} with a summary and conclusions.

@@

@@

Overlapping batch means reuses a subset of the observations from one batch to form the next batch. 
As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
In the nonoverlapping case, there are only two batches:
% the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
$y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$, and so on.  
This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
It is possible to vary the amount of overlap between neighboring batches. 
This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
%
The overlapping batch means 
%formed using the batch nonoverlap parameter $1 \leq \gamma < m$ 
are no longer independent. 
However, by simply reusing the data in this fashion one obtains a better variance estimator. 
That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
%the overlapping estimator has 
a lower asymptotic variance than its nonoverlapping counterpart.

@@

The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $0\leq \gamma< m$ relative its nonoverlapping counterpart 
%$\var{\vtm{\ybb}}$ 
depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$. 
The maximally-overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
\cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally-overlapping cases. 
Under appropriate conditions, the results of \cite{damerdji1995mean}, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
\begin{equation}
\label{eq:varvarred}
\frac{n}{m}\var{n \vartg{\ybb}} \rightarrow \beta_{\gammab} \sigma^4
\end{equation}
as the batch size $m$ and then the number of batches $n/m$ tend to infinity. 
In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches, $\beta_0 = \frac{4}{3}$ for maximally overlapping batches, and more generally, $\beta_{\gammab}$ is twice the value of 
\begin{equation} \label{eq:var_reduct_formula}
	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right),
\end{equation}
where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument.
If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
This means that the maximally-overlapping variance estimator has a variance that is two-thirds ($66.67\%$) of the nonoverlapping estimator.
As the amount of overlap decreases, the variance increases. 
When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/2$), for instance, the variance is 75\% of the nonoverlapping counterpart.

@@

The minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI; see also \citep{stockbridge_bayraksan_13}. 
The papers \citep{bayraksan_morton_09,partani2006jackknife,partani_07} discuss variations of MRP aimed to reduce bias and variance.

@@

We wish to apply overlapping batch means to MRP. 
We begin by discussing several differences in this setting compared to the classical simulation setting.  
In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
We are interested in estimating the variance of an optimality gap estimator.  
An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
%For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
%Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{subsec:nonO}).  
The nonoptimized counterparts are regular overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions. 
We establish convergence of OMRP estimators to their nonoptimized counterparts (see \S \ref{subsec:conv}--\ref{ssec:validity}); 
thereby establishing the benefits of overlapping in this context.

Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.  
In this setting, the computational effort may increase with data reuse because we need to solve a sampling problem (SP$_m$) for each batch.  
The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches, and (ii) using warm starting to quickly solve the sampling approximations with overlapping samples. 
%We use the batch nonoverlap parameter $\gamma$ as before to allow for varying degrees of overlap in OMRP. 
We examine the effect of warm starting and any resulting computational efficiency gains in \S \ref{ssec:compeff}. 
We are now ready to define the OMRP estimators.

%First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
%Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
%Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
%In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
% THIS LAST SENTENCE NEEDS TO CHANGE!

\begin{figure}[tb!]
	\centering
	\begin{tabular}{*{18}{c}}
		$\xit^1$ & $\xit^2$ & $\xit^3$ & $\xit^4$ & $\xit^5$ & $\xit^6$ & $\xit^7$ & $\xit^8$ & $\xit^9$ & $\xit^{10}$ & $\xit^{11}$ & $\xit^{12}$ & $\xit^{13}$ & $\xit^{14}$ & $\xit^{15}$ & $\xit^{16}$ & $\xit^{17}$  & $\xit^{18}$ \\
% 		First Set of Batches
		\multicolumn{6}{l}{[---------------1-----------------]} &
		\multicolumn{6}{l}{[-----------------4------------------]} &
		\multicolumn{6}{l}{[------------------7--------------------]} \\
% 		Third set of Batches
		& & \multicolumn{6}{l}{[---------------2-----------------]} &
		\multicolumn{6}{l}{[------------------5--------------------]} \\
% 		Fifth set of Batches
		& & & & \multicolumn{6}{l}{[---------------3-----------------]} &
		\multicolumn{6}{l}{[------------------6--------------------]} \\
	\end{tabular}
	\caption{Visual representation of overlapping batches with $n = 18$, $m = 6$, and $\gamma = 2$.  
        The brackets show which observations are used in each batch, and the numbers inside each bracket show the batch number $j$.}
	\label{fig:overlap_nonint}
\end{figure}

@@

The results on overlapping batch means discussed in \S \ref{ssec:overlap} occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$, as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  
In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
The OMRP estimators are defined as follows:
\begin{align}
	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
	VG_l & = \dfrac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
\end{align}

@@

The motivation behind forming $\gbb_l$ by taking into account $B(i)$ is to give each observation $\xit^i$ equal weight. 
This is because we want to be as close to a standard mean estimator (e.g., $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^i$) as possible.
With this definition of $\gbb_l$, when $\xs_j= \xs$ for all $j= 1, 2, \dots, \nbl$, we have $\gbb_l$ equal to its nonoptimized counterpart given in (\ref{eq:dbb}), which is the standard mean estimator. 
This fact is key in establishing the theoretical results presented in the next section. 
This choice of $\gbb_l$, however, may not be guaranteed to be nonnegative.
In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping. 
%In our computational results, however, we did not observe any negative values of $\gbb_l$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymptotic Validity of the Confidence Intervals}
\label{ssec:validity}
